Block Bootstrap for Time Series

### 2022-01-28 ARSimulation.Rmd
Began Writing Function
Randomly Select Single Point

Ts.boot2 is plotted
```{r, echo = False}
plot(ts.boot2, type = "l")
```

>>>>

Ts.boot2 is plotted
```{r, echo = False}
plot(ts.boot2, type = "l")
```
We need to start with a sample of a certain size B of consecutive points from a time series ts.series. First we need to randomly select a single point in the time series, and we can do this by selecting a number between 1 and 100.

```{r, echo = False}
ts.sim <- arima.sim(list(order = c(1, 0, 0), ar = 0.5), n = 100) 
single_point <- function(ts.series, B, b, overlap)
{
  point1 <- sample(c(1:length(ts.series)), 1, replace = T)
  print(point1)
}
bootstrap(ts.sim, 0, 0, F)
```
